### 2016-09-09 GPCE2016/sections/Introduction.tex
cite technical report

\item {\bf Applications and case studies:} we illustrate the usefulness of IB
  through various examples and case studies. The implementation, case
  studies, and an extended
  technical report with a formal translation to Java are
  online. \footnote{\url{https://github.com/YanlinWang/classless-java}}

>>>>

\item {\bf Applications and case studies:} we illustrate the usefulness of IB
  through various examples and case studies\footnote{\url{https://github.com/YanlinWang/classless-java}}. 
  An extended version with a formal translation to Java can be found in the 
  companion technical report~\cite{classless}.
